The Types and Driving Forces of Modifications in the Evolution of an API

### 2015-05-18 thesis/paper.tex
More minor changes to text
RQ2 RQ3 swap

\subsection{Research Questions} \label{rqs}
\begin{description}
\item[\textbf{RQ1}] How do companies actively drive API evolution?
\item[\textbf{RQ2}] To what extent can we reverse engineer API change decisions?
\item[\textbf{RQ3}] How do APIs ``passively'' evolve?

@@

%Reasons for choosing case study
The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context. The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case, runeson2009guidelines, yin2013case, robson2002real}. An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}. An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ2}.

@@

%RQ2
To allow us to answer \textbf{RQ2}, we compared our analysis and interpretation of the trends identified prior, against what was expressed by the API architect, during the interview. Success was determined by comparing the inter-rater reliability, by performing calculating Cohen's Kappa gathered data.

%RQ3
The analysis of the changes and trends, combined with the information gathered from the interview, allowed us to answer \textbf{RQ3} by determining if Lehman's Laws apply to the changes made to the API.

@@

\section{Results} \label{results} 
This section will present the findings of our study. The results related to \textbf{RQ1} and \textbf{RQ2} are introduced in Section \ref{results_rq1}, and the results of \textbf{RQ3} are presented in Section \ref{results_RQ3}

@@

\smallskip \noindent
\textbf{Preventive  }
%Define
Preventive changes are defined to be changes that attempt to avoid future maintenance. This should not be confused with changes that attempt to make the current state of the system more maintainable.
%Data and examples
Two changes were identified to be Preventive types of change. A new error handling system was one of these changes. It is unclear from version 1.4 what error handling was in place, however, version 2.0 saw the addition of specific error handling modules and functions. According to the interview, the error handling change coincided with the inclusion of more Glib features, which the new error handling system uses. The redesign of the system to use more interfaces was also deemed as a preventive change. Using interfaces to access modules helps to make them more maintainable and more easily extendable, which is a good example of a preventive change.
%Concusion
Preventive types of change appear to drive the evolution of an API more strongly than other types of changes do. This could be due to the fact that as the API grows, the need for higher maintenance also increase, a fact that also seems to be supported by Lehman's laws.

@@

\subsection{RQ2 Results}

@@

\subsection{RQ3 Results} \label{results_RQ3} 
\noindent
RQ3: \textbf{How do APIs ``passively'' evolve?}
\smallskip

The results related to \textbf{RQ3} are structured around each of Lehman's laws of software evolution \cite{lehman90sview} and to what extent our findings show that the laws apply to platform APIs. A summary of our findings can be seen in Table \ref{table:lehman}.

@@

%Implications for Industry
%Implications for Academia
%Future work / suggestions based on this RQ?

>>>>

\subsection{Research Questions} \label{rqs}
\begin{description}
\item[\textbf{RQ1}] How do companies actively drive API evolution?
\item[\textbf{RQ2}] How do APIs ``passively'' evolve?
\item[\textbf{RQ3}] To what extent can we reverse engineer API change decisions?

@@

%Reasons for choosing case study
The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context. The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case, runeson2009guidelines, yin2013case, robson2002real}. An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}. An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ3}.

@@

%RQ2
The analysis of the changes and trends, combined with the information gathered from the interview, allowed us to answer \textbf{RQ2} by determining if Lehman's Laws apply to the changes made to the API.

%RQ3
To allow us to answer \textbf{RQ3}, we compared our analysis and interpretation of the trends identified prior, against what was expressed by the API architect, during the interview. Success was determined by comparing the inter-rater reliability, by performing calculating Cohen's Kappa gathered data.

@@

\section{Results} \label{results} 
%%Write new

@@

\smallskip \noindent
\textbf{Preventive  }
%Define
Preventive changes are defined to be changes that attempt to avoid future maintenance. This should not be confused with changes that attempt to make the current state of the system more maintainable.
%Data and examples
Two changes were identified to be Preventive types of change. A new error handling system was one of these changes. It is unclear from version 1.4 what error handling was in place, however, version 2.0 added specific error handling modules and functions. According to the interview, the error handling change coincided with the inclusion of more Glib features, which the new error handling system uses. The redesign of the system to use more interfaces was also deemed as a preventive change. Using interfaces to access modules helps to make them more maintainable and more easily extendable, which is a good example of a preventive change.
%Concusion
Preventive types of change appear to drive the evolution of an API more strongly than other types of changes do. This could be due to the fact that as the API grows, the need for higher maintenance also increase, a fact that also seems to be supported by Lehman's laws.

@@

\subsection{RQ3 Results}

@@

\subsection{RQ2 Results} \label{results_RQ2} 
\noindent
RQ2: \textbf{How do APIs ``passively'' evolve?}
\smallskip

The results related to \textbf{RQ2} are structured around each of Lehman's laws of software evolution \cite{lehman90sview} and to what extent our findings show that the laws apply to platform APIs. A summary of our findings can be seen in Table \ref{table:lehman}.

@@

%Implications for Industry
%Important to understand the types of changes they are making so that they can better plan for them in the future. Design around them, design for them? Design to minimise them? Spin this into a design problem? **According to Lehman's laws, systems must keep changing otherwise they decline in quality. If they wish to maintain the quality of their system and provide new features, it would be helpful to know what kinds of changes are common for their APIs.
%Implications for Academia
%Future work / suggestions based on this RQ?
